<!-- R Commander Markdown Template -->

Replace with Main Title
=======================

### Savanna

### `r as.character(Sys.Date())`

```{r echo=FALSE}
# include this code chunk as-is to set options
knitr::opts_chunk$set(comment=NA, prompt=TRUE, out.width=750, fig.height=8, fig.width=8)
library(Rcmdr)
library(car)
library(RcmdrMisc)
```
## Please modify this section of the code to change to your own directory. Make absolutely sure that you have all 
#of the relevant associated data files in your directory as well.

```{r}
setwd("C:/Users/Savanna/Documents/1NewRDirectory")
```

#Load Carnforth or Warton Data#

```{r}
CarnforthPlantChemistry <- read.csv("CarnforthPlantChemistry.csv")
```


```{r}
str(CarnforthPlantChemistry)
```


```{r}
CarnforthPlantSpecies <- read.csv("CarnforthPlantSpecies.csv")
```


```{r}
str(CarnforthPlantSpecies)
```

#Convert data into dataframes for analyses#

```{r}
CarnforthPlantSpecies1 <- data.frame(CarnforthPlantSpecies)
```

```{r}
CarnforthPlantChemistry1 <- data.frame(CarnforthPlantChemistry)
```

#Now to run a series of analyses to assess Renyi biodiversity values for different concentrations of specific elements,
#as well as different pH levels.

```{r}
CarnforthPlantChemistry1$pH <- as.factor(CarnforthPlantChemistry1$pH_level)
```

```{r}
Carnforth.pH <- renyicomp(CarnforthPlantSpecies1, y=CarnforthPlantChemistry1, factor = 'pH',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Carnforth.pH)
```

```{r}
Carnforth.pH
```

```{r}
CarnforthPlantChemistry1$Al2O3 <- as.factor(CarnforthPlantChemistry1$Al2O3)
```

```{r}
Carnforth.Al2O3 <- renyicomp(CarnforthPlantSpecies1, y=CarnforthPlantChemistry1, factor = 'Al2O3',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Carnforth.Al2O3)
```

```{r}
Carnforth.Al2O3
```

```{r}
CarnforthPlantChemistry1$SiO2 <- as.factor(CarnforthPlantChemistry1$SiO2)
```

```{r}
Carnforth.SiO2 <- renyicomp(CarnforthPlantSpecies1, y=CarnforthPlantChemistry1, factor = 'SiO2',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Carnforth.SiO2)
```

```{r}
Carnforth.SiO2
```

```{r}
CarnforthPlantChemistry1$Fe2O3 <- as.factor(CarnforthPlantChemistry1$Fe2O3)
```

```{r}
Carnforth.Fe2O3 <- renyicomp(CarnforthPlantSpecies1, y=CarnforthPlantChemistry1, factor = 'Fe2O3',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Carnforth.Fe2O3)
```

```{r}
Carnforth.Fe2O3
```

```{r}
CarnforthPlantChemistry1$CaO <- as.factor(CarnforthPlantChemistry1$CaO)
```

```{r}
Carnforth.CaO <- renyicomp(CarnforthPlantSpecies1, y=CarnforthPlantChemistry1, factor = 'CaO',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Carnforth.CaO)
```

```{r}
Carnforth.CaO
```

```{r}
CarnforthPlantChemistry1$MgO <- as.factor(CarnforthPlantChemistry1$MgO)
```

```{r}
Carnforth.MgO <- renyicomp(CarnforthPlantSpecies1, y=CarnforthPlantChemistry1, factor = 'MgO',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Carnforth.MgO)
```

```{r}
Carnforth.MgO
```

```{r}
CarnforthPlantChemistry1$Na2O <- as.factor(CarnforthPlantChemistry1$Na2O)
```

```{r}
Carnforth.Na2O <- renyicomp(CarnforthPlantSpecies1, y=CarnforthPlantChemistry1, factor = 'Na2O',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Carnforth.Na2O)
```

```{r}
Carnforth.Na2O
```

```{r}
CarnforthPlantChemistry1$K2O <- as.factor(CarnforthPlantChemistry1$K2O)
```

```{r}
Carnforth.K2O <- renyicomp(CarnforthPlantSpecies1, y=CarnforthPlantChemistry1, factor = 'K2O',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Carnforth.K2O)
```

```{r}
Carnforth.K2O
```

```{r}
CarnforthPlantChemistry1$Cr2O3 <- as.factor(CarnforthPlantChemistry1$Cr2O3)
```

```{r}
Carnforth.Cr2O3 <- renyicomp(CarnforthPlantSpecies1, y=CarnforthPlantChemistry1, factor = 'Cr2O3',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Carnforth.Cr2O3)
```

```{r}
Carnforth.Cr2O3
```

```{r}
CarnforthPlantChemistry1$TiO2 <- as.factor(CarnforthPlantChemistry1$TiO2)
```

```{r}
Carnforth.TiO2 <- renyicomp(CarnforthPlantSpecies1, y=CarnforthPlantChemistry1, factor = 'TiO2',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Carnforth.TiO2)
```

```{r}
Carnforth.TiO2
```

```{r}
CarnforthPlantChemistry1$MnO <- as.factor(CarnforthPlantChemistry1$MnO)
```

```{r}
Carnforth.MnO <- renyicomp(CarnforthPlantSpecies1, y=CarnforthPlantChemistry1, factor = 'MnO',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Carnforth.MnO)
```

```{r}
Carnforth.MnO
```

```{r}
CarnforthPlantChemistry1$P2O5 <- as.factor(CarnforthPlantChemistry1$P2O5)
```

```{r}
Carnforth.P2O5 <- renyicomp(CarnforthPlantSpecies1, y=CarnforthPlantChemistry1, factor = 'P2O5',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Carnforth.P2O5)
```

```{r}
Carnforth.P2O5
```

```{r}
CarnforthPlantChemistry1$SrO <- as.factor(CarnforthPlantChemistry1$SrO)
```

```{r}
Carnforth.SrO <- renyicomp(CarnforthPlantSpecies1, y=CarnforthPlantChemistry1, factor = 'SrO',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Carnforth.SrO)
```

```{r}
Carnforth.SrO
```

```{r}
CarnforthPlantChemistry1$BaO <- as.factor(CarnforthPlantChemistry1$BaO)
```

```{r}
Carnforth.BaO <- renyicomp(CarnforthPlantSpecies1, y=CarnforthPlantChemistry1, factor = 'BaO',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Carnforth.BaO)
```

```{r}
Carnforth.BaO
```


```{r}
CarnforthPlantChemistry1$As <- as.factor(CarnforthPlantChemistry1$As)
```

```{r}
Carnforth.As <- renyicomp(CarnforthPlantSpecies1, y=CarnforthPlantChemistry1, factor = 'As',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Carnforth.As)
```

```{r}
Carnforth.As
```

```{r}
CarnforthPlantChemistry1$Co <- as.factor(CarnforthPlantChemistry1$Co)
```

```{r}
Carnforth.Co <- renyicomp(CarnforthPlantSpecies1, y=CarnforthPlantChemistry1, factor = 'Co',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Carnforth.Co)
```

```{r}
Carnforth.Co
```

```{r}
CarnforthPlantChemistry1$Pb <- as.factor(CarnforthPlantChemistry1$Pb)
```

```{r}
Carnforth.Pb <- renyicomp(CarnforthPlantSpecies1, y=CarnforthPlantChemistry1, factor = 'Pb',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Carnforth.Pb)
```

```{r}
Carnforth.Pb
```

```{r}
CarnforthPlantChemistry1$S <- as.factor(CarnforthPlantChemistry1$S)
```

```{r}
Carnforth.S <- renyicomp(CarnforthPlantSpecies1, y=CarnforthPlantChemistry1, factor = 'S',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Carnforth.S)
```

```{r}
Carnforth.S
```

```{r}
CarnforthPlantChemistry1$V <- as.factor(CarnforthPlantChemistry1$V)
```

```{r}
Carnforth.V <- renyicomp(CarnforthPlantSpecies1, y=CarnforthPlantChemistry1, factor = 'V',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Carnforth.V)
```

```{r}
Carnforth.V
```

#Loading Hodbarrow Data#

```{r}
HodbarrowPlantSpecies <- read.csv("HodbarrowPlantSpecies.csv")
```


```{r}
str(HodbarrowPlantSpecies)
```


```{r}
HodbarrowPlantChemistry <- read.csv("HodbarrowPlantChemistry.csv")
```


```{r}
str(HodbarrowPlantChemistry)
```

#Converting data to dataframes for analyses#

```{r}
HodbarrowPlantSpecies1 <- data.frame(HodbarrowPlantSpecies)
```


```{r}
HodbarrowPlantChemistry1 <- data.frame(HodbarrowPlantChemistry)
```

#Now to run a series of analyses to assess Renyi biodiversity values for different concentrations of specific elements,
#as well as different pH levels.

```{r}
HodbarrowPlantChemistry1$pH <- as.factor(HodbarrowPlantChemistry1$pH_level)
```


```{r}
Hodbarrow.pH <- renyicomp(HodbarrowPlantSpecies1, y=HodbarrowPlantChemistry1, factor = 'pH_level',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Hodbarrow.pH)
```

```{r}
Hodbarrow.pH
```

```{r}
HodbarrowPlantChemistry1$SiO2 <- as.factor(HodbarrowPlantChemistry1$SiO2)
```


```{r}
Hodbarrow.SiO2 <- renyicomp(HodbarrowPlantSpecies1, y=HodbarrowPlantChemistry1, factor = 'SiO2',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Hodbarrow.SiO2)
```

```{r}
Hodbarrow.SiO2
```

```{r}
HodbarrowPlantChemistry1$Al2O3 <- as.factor(HodbarrowPlantChemistry1$Al2O3)
```


```{r}
Hodbarrow.Al2O3 <- renyicomp(HodbarrowPlantSpecies1, y=HodbarrowPlantChemistry1, factor = 'Al2O3',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Hodbarrow.Al2O3)
```

```{r}
Hodbarrow.Al2O3
```

```{r}
HodbarrowPlantChemistry1$Fe2O3 <- as.factor(HodbarrowPlantChemistry1$Fe2O3)
```


```{r}
Hodbarrow.Fe2O3 <- renyicomp(HodbarrowPlantSpecies1, y=HodbarrowPlantChemistry1, factor = 'Fe2O3',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Hodbarrow.Fe2O3)
```

```{r}
Hodbarrow.Fe2O3
```

```{r}
HodbarrowPlantChemistry1$CaO <- as.factor(HodbarrowPlantChemistry1$CaO)
```


```{r}
Hodbarrow.CaO <- renyicomp(HodbarrowPlantSpecies1, y=HodbarrowPlantChemistry1, factor = 'CaO',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Hodbarrow.CaO)
```

```{r}
Hodbarrow.CaO
```

```{r}
HodbarrowPlantChemistry1$MgO <- as.factor(HodbarrowPlantChemistry1$MgO)
```


```{r}
Hodbarrow.MgO <- renyicomp(HodbarrowPlantSpecies1, y=HodbarrowPlantChemistry1, factor = 'MgO',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Hodbarrow.MgO)
```

```{r}
Hodbarrow.MgO
```

```{r}
HodbarrowPlantChemistry1$Na2O <- as.factor(HodbarrowPlantChemistry1$Na2O)
```


```{r}
Hodbarrow.Na2O <- renyicomp(HodbarrowPlantSpecies1, y=HodbarrowPlantChemistry1, factor = 'Na2O',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Hodbarrow.Na2O)
```

```{r}
Hodbarrow.Na2O
```

```{r}
HodbarrowPlantChemistry1$K2O <- as.factor(HodbarrowPlantChemistry1$K2O)
```


```{r}
Hodbarrow.K2O <- renyicomp(HodbarrowPlantSpecies1, y=HodbarrowPlantChemistry1, factor = 'K2O',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Hodbarrow.K2O)
```

```{r}
Hodbarrow.K2O
```

```{r}
HodbarrowPlantChemistry1$Cr2O3 <- as.factor(HodbarrowPlantChemistry1$Cr2O3)
```


```{r}
Hodbarrow.Cr2O3 <- renyicomp(HodbarrowPlantSpecies1, y=HodbarrowPlantChemistry1, factor = 'Cr2O3',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Hodbarrow.Cr2O3)
```

```{r}
Hodbarrow.Cr2O3
```

```{r}
HodbarrowPlantChemistry1$TiO2 <- as.factor(HodbarrowPlantChemistry1$TiO2)
```


```{r}
Hodbarrow.TiO2 <- renyicomp(HodbarrowPlantSpecies1, y=HodbarrowPlantChemistry1, factor = 'TiO2',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Hodbarrow.TiO2)
```

```{r}
Hodbarrow.TiO2
```

```{r}
HodbarrowPlantChemistry1$MnO <- as.factor(HodbarrowPlantChemistry1$MnO)
```


```{r}
Hodbarrow.MnO <- renyicomp(HodbarrowPlantSpecies1, y=HodbarrowPlantChemistry1, factor = 'MnO',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Hodbarrow.MnO)
```

```{r}
Hodbarrow.MnO
```

```{r}
HodbarrowPlantChemistry1$P2O5 <- as.factor(HodbarrowPlantChemistry1$P2O5)
```


```{r}
Hodbarrow.P2O5 <- renyicomp(HodbarrowPlantSpecies1, y=HodbarrowPlantChemistry1, factor = 'P2O5',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Hodbarrow.P2O5)
```

```{r}
Hodbarrow.P2O5
```

```{r}
HodbarrowPlantChemistry1$SrO <- as.factor(HodbarrowPlantChemistry1$SrO)
```


```{r}
Hodbarrow.SrO <- renyicomp(HodbarrowPlantSpecies1, y=HodbarrowPlantChemistry1, factor = 'SrO',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Hodbarrow.SrO)
```

```{r}
Hodbarrow.SrO
```

```{r}
HodbarrowPlantChemistry1$BaO <- as.factor(HodbarrowPlantChemistry1$BaO)
```


```{r}
Hodbarrow.BaO <- renyicomp(HodbarrowPlantSpecies1, y=HodbarrowPlantChemistry1, factor = 'BaO',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Hodbarrow.BaO)
```

```{r}
Hodbarrow.BaO
```

```{r}
HodbarrowPlantChemistry1$As <- as.factor(HodbarrowPlantChemistry1$As)
```


```{r}
Hodbarrow.As <- renyicomp(HodbarrowPlantSpecies1, y=HodbarrowPlantChemistry1, factor = 'As',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Hodbarrow.As)
```

```{r}
Hodbarrow.As
```

```{r}
HodbarrowPlantChemistry1$Co <- as.factor(HodbarrowPlantChemistry1$Co)
```


```{r}
Hodbarrow.Co <- renyicomp(HodbarrowPlantSpecies1, y=HodbarrowPlantChemistry1, factor = 'Co',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Hodbarrow.Co)
```

```{r}
Hodbarrow.Co
```

```{r}
HodbarrowPlantChemistry1$Pb <- as.factor(HodbarrowPlantChemistry1$Pb)
```


```{r}
Hodbarrow.Pb <- renyicomp(HodbarrowPlantSpecies1, y=HodbarrowPlantChemistry1, factor = 'Pb',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Hodbarrow.Pb)
```

```{r}
Hodbarrow.Pb
```

```{r}
HodbarrowPlantChemistry1$S <- as.factor(HodbarrowPlantChemistry1$S)
```


```{r}
Hodbarrow.S <- renyicomp(HodbarrowPlantSpecies1, y=HodbarrowPlantChemistry1, factor = 'S',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Hodbarrow.S)
```

```{r}
Hodbarrow.S
```

```{r}
HodbarrowPlantChemistry1$V <- as.factor(HodbarrowPlantChemistry1$V)
```


```{r}
Hodbarrow.V <- renyicomp(HodbarrowPlantSpecies1, y=HodbarrowPlantChemistry1, factor = 'V',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Hodbarrow.V)
```

```{r}
Hodbarrow.V
```
